The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-10 manuscript/5pillars_docx.Rmd
Sam moved to acknowledgement - confirmed via email

---
title: "The five pillars of computational reproducibility: Bioinformatics and beyond"
author: "Mark Ziemann, Samuel S. Minot, Pierre Poulain, Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
bibliography: 5pillars.bib
csl: plos-computational-biology.csl
---

Mark Ziemann<sup>1*</sup>, Samuel S. Minot<sup>2</sup>, Pierre Poulain<sup>3</sup>,
Anusuiya Bora<sup>1</sup>

<details><summary>Author information (*click to expand*)</summary><p>

@@

2. Fred Hutchinson Cancer Center, Seattle, USA.

3. Université Paris Cité, CNRS, Institut Jacques Monod, Paris, France.

Correspondance: m.ziemann@deakin.edu.au

| Author | ORCID |
| --- | --- |
| Mark Ziemann | 0000-0002-7688-6974 |
| Samuel S. Minot | 0000-0003-1639-3905 |
| Pierre Poulain | 0000-0003-4177-3619 |
| Anusuiya Bora | 0009-0006-2908-1352 |

</details>
</p>
Source: https://github.com/markziemann/5pillars/blob/main/manuscript/5pillars.Rmd

@@

@@

We are grateful to individuals who provided feedback on an earlier draft of the concept including
Dr Aziz Khan (Stanford University),
Dr Sriganesh Srihari (QIMR Berghofer Medical Research Institute),
Dr Barbara Zdrazil (EMBL-EBI) and
Dr Irene López Santiago (EMBL-EBI).
Special thanks to Dr Altuna Akalin (Max Delbrück Center, Germany) and
Dr Simon Tournier (Paris Cité University, France) for advice on Guix.

This research was supported by use of the Nectar Research Cloud, a collaborative Australian research
platform supported by the NCRIS-funded Australian Research Data Commons (ARDC).

@@

**Samuel S. Minot** works as a Staff Scientist at Fred Hutchinson Cancer Center within the Vaccine and
Infectious Disease Division.
His research is focused on human microbiota associations with human health and disease.

>>>>

---
title: "The five pillars of computational reproducibility: Bioinformatics and beyond"
author: "Mark Ziemann, Pierre Poulain, Anusuiya Bora"
date: "`r Sys.Date()`"
output: word_document
code_folding: hide
fig_width: 7
fig_height: 6
bibliography: 5pillars.bib
csl: plos-computational-biology.csl
---

Mark Ziemann<sup>1*</sup>, Pierre Poulain<sup>2</sup>, Anusuiya Bora<sup>1</sup>

@@

2. Université Paris Cité, CNRS, Institut Jacques Monod, Paris, France.

* Correspondance: m.ziemann@deakin.edu.au

| Author | ORCID |
| --- | --- |
| Mark Ziemann | 0000-0002-7688-6974 |
| Pierre Poulain | 0000-0003-4177-3619 |
| Anusuiya Bora | 0009-0006-2908-1352 |

Source: https://github.com/markziemann/5pillars/blob/main/manuscript/5pillars.Rmd

<br>

@@

<br>

@@

We are grateful to individuals who provided feedback on an earlier draft of the concept including
Dr Aziz Khan (Stanford University),
Dr Sriganesh Srihari (QIMR Berghofer Medical Research Institute),
Dr Barbara Zdrazil (EMBL-EBI) and
Dr Irene López Santiago (EMBL-EBI).
Special thanks to Dr Altuna Akalin (Max Delbrück Center, Germany) and
Dr Simon Tournier (Paris Cité University, France) for advice on Guix.
We appreciate advice on Python notebooks from Dr Samuel S. Minot (Fred Hutchinson Cancer Center).
This research was supported by use of the Nectar Research Cloud, a collaborative Australian research
platform supported by the NCRIS-funded Australian Research Data Commons (ARDC).

<br>

@@
